%-----       letter       ---------------------------------------------------------
% recipient data
\recipient{Wolters Kluwer CCH Canada}{90 Sheppard Ave E\\North York, ON M2N 6X1}
\date{September 23, 2016}
\date{\today}
\opening{Dear Hiring Manager,}
\closing{Thanking you.\\Yours truly,}
\enclosure[Encl:]{Résumé}          % use an optional argument to use a string other than "Enclosure", or redefine \enclname
\makelettertitle

\underline{Subject: Software Developer}
\newline 

%Why you are writing. How do you qualify for the job
Regarding the \emph{Software Developer} position currently listed on \href{https://www.linkedin.com/jobs/view/205365298?refId=6f630c4d-b372-4e20-bc6a-87deafcbac25}{\emph{LinkedIn}}, please find enclosed my resume for your consideration. I am extremely passionate about designing and coding software applications, and derive immense satisfaction in solving complex technical problems. As listed under the \emph{Summary of Qualifications} and \emph{Work Experience} sections in my résumé, I have considerable experience in .NET, C\#, XML and  SQL, hands-on experience in developing web applications, and in my previous roles have effectively collaborated with Engineering, Management, Marketing and other functional teams to create enterprise application software as solutions to complex technical problems.

%What you have to offer. Summarize "Why they should hire you" - What you can do for them and skills you would use (2-3 sentences). What is your present status, since your last job. Relate relevant experience/skills and accomplishments to the position at hand.
I quit my most recent job on Feb 29, 2016, because I was immigrating to Canada in the first week of April, 2016. I have been actively looking for a job here since, and I am available to start working as soon as required. In my previous role as \emph{Associate Software Engineer} at \emph{KLA-Tencor} (listed under \emph{Work Experience} in résumé), I was awarded the \emph{Outstanding Achievement by a New College Graduate} award for storyboarding, designing and implementing a new product (in C\# .NET using the WPF framework and WinForms) that was a huge success with Intel (one of KLA-Tencor's customers). Auxiliary responsibilities included supporting bug fixes, contributing to technical documentation (including design diagrams, class diagrams, sequence diagrams), participating in code review sessions, and planning project roadmap and estimation. In my role as \emph{Team Lead} for \emph{Sockmonkey, NIT Calicut} (listed under \emph{Work Experience} in résumé), I led a team in designing (database entities, their relationships, overall application architecture) and implementing a robust web application for managing an inter-university competition.


%Closing paragraph
I thank you for considering my resume. I'm very enthusiastic about the opportunity to bring my drive to succeed and my passion for solving challenging complex problems to your company. I look forward to hearing from you to discuss my application and to arrange an interview, and will be reachable by email at addy689@gmail.com

\makeletterclosing

%\clearpage\end{CJK*}                              % if you are typesetting your resume in Chinese using CJK; the \clearpage is required for fancyhdr to work correctly with CJK, though it kills the page numbering by making \lastpage undefined